Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
fucking rewrite

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash \scriptsize{482457bf2bbb5673fbab5f663da5fd3d78ed132f} } version of the Moses decoder taken from the github repository.

>>>>

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash \scriptsize{bc5f8d15c6ce4bc678ba992860bfd4be6719cee8} } version of the Moses decoder taken from the github repository.
